\documentclass[11pt]{book}
%Gummi|062|=)
\title{\textbf{Programming Tasks}}
\author{Guy Edwards}
\date{30th March 2012}
\begin{document}

\section{Visualisation}

\subsection{Problem Definition}

\paragraph{} You are asked to improve the visualisation and immersion of your software. Add audio and visual clues to events in the simulation.

\subsection{Requirements}

\begin{enumerate}
\item Call a text to speech library for each of
    \begin{enumerate}
    \item Taking off
    \item Landing
    \item Searching for objective
    \item Evading
    \item Fuel low
    \item Target sighted
    \item Objective complete
    \item Being targeted
    \item Mission complete, returning to base
    \end{enumerate}
\item Record and add sound effects where it helps a user perceive what is going on (such as landing gear servos)
\item Add an option to disable sound except for from the currently selected entity
\item Add previous position trails to help judge movement
\end{enumerate}

\subsection{Why Are We Doing This?}

\paragraph{} There's only so much information that can be taken in visually at a given time, audio clues are another method of communicating information and add interest to your software.

\paragraph{} The quality of the free text to speech voices can be a little disappointing but it's important to demonstrate the application.

\subsection{Bonus Tasks}

\begin{itemize}
\item Can you make sound effects for the animals when photographed?
\item Can you give the Red and Blue UAV's different voices?
\item Can you make the voices on each team similar (same accent perhaps) but different (tone and pitch perhaps)?
\end{itemize}

\end{document}
