\documentclass[11pt]{book}
%Gummi|062|=)
\title{\textbf{Programming Tasks}}
\author{Guy Edwards}
\date{30th March 2012}
\begin{document}

\section{More War Part II}

\subsection{Problem Definition}

\paragraph{} A games designer approaches you to evaluate if your software might be worth purchasing to incorporate into their next game, perhaps employing you and paying your former employer to license the code at the same time.

\subsection{Requirements}

\begin{enumerate}
\item In the GUI allow selection of the UAV versus UAV mode
\item Whenever a UAV is caught in camera sights for a given length of time it is removed from play
\item In this mode allow a perpetual sub mode whereby a new UAV is launched from the airfield whenever one is removed from play
\item Track successful UAV camera shots per team, show these scores in a GUI interface
\item Allow multiple (configurable) UAV's in the air at once, with a configurable upper limit on the number in the air
\item Create more than one type of UAV - bomber type (targeting the airfield), and fighter type (targeting UAVs)
\end{enumerate}

\subsection{Why Are We Doing This?}

\paragraph{} This is an example of changing the purpose of your software to meet new demands (new applications or new clients).

\paragraph{} The more care you take in making your software modular, and logically divided internally, the easier it will be to adapt it for changes like this.

\paragraph{} It's also a good behavioural testing environment. Take care to judge if the aircraft are behaving like aircraft you see in videos. If a certain manover looks unrealistic then something might be wrong and need corrective work. 

\subsection{Bonus Tasks}

\begin{itemize}
\item Introduce missile objects with limited numbers per plane, limited flight time, specific turn radius. If you're unsure how to do this, think of these as a UAV from one of the early projects, with no camera but a proximity radius, defined mission and starting point set on the location of the launching UAV.
\item Watch videos (youtube perhaps) of aircraft dogfighting, do the aircraft manover in a similar fashion?
\end{itemize}

\end{document}
